Time slice analyses

### 2017-11-27 analyses/02-time-slice-analyses.Rmd
Add time slice analyses for all datasets

```{r, eval = TRUE, warning = FALSE}
## Run the function for Beck data
slug <- "Beck2014"

@@

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", "Beck2014" ,".Rda"))

@@

>>>>

```{r, eval = TRUE, warning = FALSE}

@@

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", slug ,".Rda"))

@@

Running the analyses for other datasets
===================================================
Ideally we'd have written functions to do this, and/or a big old loop. But each dataset was slightly different so we've dealt with each individually.

Wright 2017
-----------
```{r}
## Choose a slug
slug <- "Wright2017"

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age as defined in Wright 2017
tree$root.time <- 484.4

## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
readRDS(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix
morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points

## Run the disparity analyses
## Ages (rarefied to 3 taxa only)
out1 <- run.all.disparity.wrapper(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances),
                                metric.name = "sum_var", rarefaction = FALSE)

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", slug ,".Rda"))

Bapst et al 2016 Biol Letters
-----------

```{r}
slug <- "Bapst2016"

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age (max tree age date)
tree$root.time <- max(tree.age(tree)[, 1])

## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
readRDS(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix
morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points

## Run the disparity analyses
## Ages (rarefied to 3 taxa only)
out1 <- run.all.disparity.wrapper(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances),
                                metric.name = "sum_var", rarefaction = FALSE)

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", slug ,".Rda"))

Heath et al bears
-----------

```{r}
slug <- "bears"

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age (max tree age date)
tree$root.time <- max(tree.age(tree)[, 1])

## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
readRDS(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix
morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points

## Run the disparity analyses
## Ages (rarefied to 3 taxa only)
out1 <- run.all.disparity.wrapper(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances),
                                metric.name = "sum_var", rarefaction = FALSE)

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", slug ,".Rda"))

Brusatte et al 2014 Current Biol
-----------

```{r}
slug <- "Brusatte2014"

## Loading the tree
## See "01-extract-data-for analyses.Rmd" for how we cleaned these
tree <- read.nexus(paste0("../data/processed/tree.", slug, ".tre"))
## Add root age (max tree age date)
tree$root.time <- max(tree.age(tree)[, 1])

## Loading the distance matrices
## See "01-extract-data-for analyses.Rmd" for how we made these
readRDS(paste0("../data/processed/distance_matrix.", slug ,".Rda"))

## Ordinating the matrix
morphospace <- cmdscale(matrix_dist, k = nrow(matrix_dist) - 2, add = TRUE)$points

## Run the disparity analyses
## Ages (rarefied to 3 taxa only)
out1 <- run.all.disparity.wrapper(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances),
                                metric.name = "sum_var", rarefaction = FALSE)

## Save results to output folder
saveRDS(out1, file = paste0("../outputs/age.", slug ,".Rda"))
